Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-05-18 paper.tex
smaller extrapolation figure. still need to make things more legible by changing colors hands rescaling the pictures

\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level edits to the figure generated by that program. 
For example,
we can change all of the circles to squares or make all of the lines be dashed.
We can also \textbf{extrapolate} figures
by increasing the number of times that loops are executed.~\remark{Pick a few of these to show off and put the rest in supplement?}
Extrapolating repetitive visuals patterns comes naturally to humans,
and building this ability into an application is practical:
imagine hand drawing a repetitive graphical model structure
and having our system automatically induce and extend the pattern.
Fig.~\ref{extrapolationFigure} shows extrapolations of programs synthesized from ground truth traces;
see supplement for our full set of extrapolations.

\begin{figure}
  \includegraphics[width = 8in]{figures/extrapolationMatrix.png}
  \caption{Left: hand drawings. Right: extrapolations produced by
    running different parts of different loops either forward or
    backward an extra iteration.}\label{extrapolationFigure}
  \end{figure}
%\input{extrapolations.tex}

>>>>

\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level edits to the figure generated by that program. 
For example,
we can change all of the circles to squares or make all of the lines be dashed.
We can also \textbf{extrapolate} figures
by increasing the number of times that loops are executed.
Extrapolating repetitive visuals patterns comes naturally to humans,
and building this ability into an application is practical:
imagine hand drawing a repetitive graphical model structure
and having our system automatically induce and extend the pattern.
Fig.~\ref{extrapolationFigure} shows extrapolations of programs synthesized from ground truth traces;
see supplement for our full set of extrapolations.

\begin{figure}
  \includegraphics[width = \textwidth]{figures/extrapolationMatrix.png}
  \caption{Top: hand drawings. Bottom: extrapolations produced by
running loops for extra iterations.}\label{extrapolationFigure}
  \end{figure}
%\input{extrapolations.tex}
